pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Example 1 has ESSes

Here we discuss how to interpret the results of \verb;pirouette;.
Figure \ref{fig:example_1} shows that the generative model 
gives an error distribution with a highest posterior density (HPD) 
\giovanni{probably "median" is a better word}
\richel{HPC is a valid Bayesian term I learned from the BEAST book}
at 0.015
The range of errors goes from 0.0 to 0.097 
As we know the generative model, 
this error distribution is the minimum noise that BEAST2 produces 
for that generative model.
We measure the effective samples as well, and all are well above
the recommended value of 200 \ref{drummond2015bayesian}, 
as shown in table \ref{tab:esses_example_1}.

@@

>>>>

Here we discuss how to interpret the results of \verb;pirouette;.
Figure \ref{fig:example_1} shows that the generative model 
gives an error distribution with a highest posterior density (HPD) 
\giovanni{probably "median" is a better word}
\richel{HPC is a valid Bayesian term I learned from the BEAST book}
at 0.015
The range of errors goes from 0.0 to 0.097 
As we know the generative model, 
this error distribution is the minimum noise that BEAST2 produces 
for that generative model.
We can measure the effective samples as well (not shown), 
and all ESSes are above
the recommended value of 200 \cite{drummond2015bayesian}, 
as shown in table \ref{tab:esses_example_1}.

@@

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results in detail}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
